Branchy parallelized U-net structure Branching, finetune, reparameterized, pruning paralleled branched Pruning reparameterized super-resolution model

### 2023-04-04 NTIRE 2023 RTSR Paper/PaperForReview.tex
加作者

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}
\maketitle

>>>>

\author{Daheng Yin, Baijun Chen, Mengyang Liu\\
School of Computer Science and Engineering, Southeast University, Nanjing, China\\
{\tt\small \{yindaheng98, bjchen, myliu\}@seu.edu.cn}
}
\maketitle
